---
title: "Cushioning Materials for IR"
author: "Committee on Cushioning Materials"
date: "18/03/2022"
#output: powerpoint_presentation
#output: beamer_presentation
#output: revealjs::revealjs_presentation
#output: ioslides_presentation
output:
  beamer_presentation:
    slide_level: 2
    theme: "AnnArbor"
    colortheme: "dolphin"
    fonttheme: "structurebold"
  #   
  # powerpoint_presentation:
  # reference_doc: my-styles.pptx  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## plot

```{r, cars2, fig.cap="A scatterplot.", echo=FALSE}
plot(cars)
```


## two column

:::::: {.columns}
::: {.column}
Content of the left column.
:::

::: {.column}
Content of the right column.
:::
::::::

## Cushioning Materials
- A material that provides support to the body and protects against impact. It is generally a softer material which when subjected to load will get pressed and regain the shape when the load is removed.
- It makes the posture comfortable by way of supporting the body and distributing the weight such that the blood circulation to any part of the body is not adversely affected.


## Cushioning Materials on IR : 1990-2000
- PU Foam to RDSO Spec no. C-8914 was developed in early 2000 and first revision published in April 2002 .
- C-8914 stipulated use of the material with fire barrier forsafety against fire hazard.
- Physical and Performance related Properties: The materials were required to comply to the requirements given in IS 7888 for density, tensile strength, compression set, load quotient ,indentation hardness and fatigue.
- Fire Resistant Properties: Flammability as per IS 7888 and Toxicity as per NCD 1409(Limit < 1) were inclded.


## Cushioning Materials on IR : 2000-2010
- Fire accidents in early 2000s led to a consultancy with SNCF. The recommendations made by SNCF led to inclusion of fire resistant properties defined in UIC 564-2. 
- Specification no. RDSO/2007/CG-04 was developed in 2007 as an upgraded spec for PU Foam.
- Physical and Performance related Properties: Tear Strength and Resilience were added to the properties defined in earlier spec C-8914 Rev 1.
- Fire Resistant Properties: Resistance to Spread of Flame ,Deterioration of visibility due to smoke ( As per UIC 564-2) and Limiting Oxygen Index (As per IS13501) were added.

## Cushioning Materials on IR : 2000-2010
- Development of vendors complying to the specification of PU foam could not take place as the products developed were found to e more toxic than permissible.
- It was noted that PU foam is used as Cushioning Material internationally in RDSO letter no.MC/CB/Cushion dtd.13.04.2006,however Toxicity of 1 could not be achieved on NCD 1409 scale. 
- Specification no. C-K607 was developed in April’2006 for DTBPB after initial trials in 50 coaches during 2004-2006.
- Physical and Performance related Properties: Same properties as defined for PU Foam.
- Fire Resistant Properties: Same FST properties as defined for PU Foam.
- This item met all the requirements of the specification and became regular cushioning material.

## Cushioning Materials on IR : 2000-2010


- Railways reported poor performance of DTBPB due to:
 + Reduction in Cushioning Effect with time
 + Permanent sagging
 + Uneven density and hardness
 + De-bonding and de-lamination of blocks.
 
- Review of Specification was undertaken in 2009 and limits for tensile strength, tear strength ,load quotient were increased along with density (from 50 to 60 kg/m3 ) . Further the limits for humidity ageing, loss in indentation hardness during fatigue test were reduced. An amendment was issued to the specification.
- Fire Resistant Properties: Same FST properties as defined earlier.


## Cushioning Materials on IR : 2000-2010

- Issues reported in use of DTBPB were addressed by revision in 2009 except for -   
 + Uneven hardness and density
 + Permanent set with usage particularly in GS Coaches
- Revision of Specification was made in 2011 to address these issues and the following changes were made-
 + Automated continuous line for consistent output
 + Density for GS Coaches increased to 80 kg/m3
 + De-lamination test as per ISO 8067 added   
-These changes in the specification addressed most of the issues except for permanent set which continues to be reported albeit with lesser frequency.          


---

Railway Board vide letter no. 2006/M(C)/137/20 Vol.V(Part-I) dtd.06.0.2014, relaxation in toxicity of PU Foam  up to 2.5 when wrapped with Fire Barrier Cloth was provided for use in Chair Cars, Double-Deckers and Day Coaches.
This relaxation was withdrawn vide RDSO letter no.MC/CB/Cushion/PU Foam dtd.29.12.2014.The reasons indicated were-
The use of Cushioning Material as PU foam is highlighted in PIL of Hon’ble Supreme Court.
ADG/RDSO noted that alternate Cushioning material such as Silicon Foam to be identified to overcome the problem of furnishing material.
Instructions issued in same letter to switch over to Silicon Foam specially indigenously manufactured being lower in cost.

---

In 2011 during visit of MM to USA, M/s Rogers presented Silicon Foam as a Cushioning material having excellent fire resistance and comfort indices along with long life of 10 years.
RDSO was directed vide Rly Board letter no.76/M(C)/137/31 dtd.30.11.2011 to take action on MM’s inspection note .
RDSO developed specification for Silicon Foam in May 2014 RDSO/2013/CG-13 and trials were conducted in GS and LWACCN coaches. Based on trial results Railway Board directed to fit the item in 30% of Coaches manufactured at PUs vide letter no.76/M(C)/137/31 Vol(iii) dtd.16.03.2018
                   
                                                

---

In the meantime EN45545 was implemented in Europe. 
During PCME’s conference held at Secunderabad in April, 2019 and PCME’s meeting on higher priority items held on 28-29th Aug, 2019 at New Delhi, it was decided to use PU foam complying to EN45545 in 70% of the coaches.
This decision was forwarded to RDSO for technical scrutiny. RDSO vide letter no.MC/CB/Cushion/PU Foam dtd.16.08.2019 gave its agreement to the proposal.
Railway Board vide letter no.2017/M(C)/142/4 pt.IV dtd.16.09.2019 issued instructions for use of Silicone foam on 30% coaches and PU Foam toEN45545 in 70% of the coaches.  MCF was directed to define physical and Performance related properties and make specification and also develop vendors.
MCF issued the specification in October’2019 for PU Foam complying to EN45545.                                             

---

Vendor development activity was undertaken by MCF and M/s Metzler, Germany and M/s Sheela Foam were listed as Developmental Vendors in Feb’2020.
Three more vendors were approved in Sep-Oct’2021-

          1. M/s NTF (India) Pvt. Ltd., Gurgaon
          2. M/s Oriental Rail Infrastructure Ltd., Thane
          3. M/s Sukata Tractor Parts,Panchkula


# Table properties
SN | Material | Tensile Strength | Elongation at Break | Humidity Ageing-Hardness loss | Fatigue-Loss in thickness after 20000 cycles | Tear Strength | Resilience | Compression set
-- | ----- | ------| ---- | ------ | ------ | ------ | ---- | ---
1 | PU Foam to CG-04 | 1.1 Kg/cm2 | 100% | 25 % Max | 10% | 0.5 N/cm min | 50 % | 10% 


2
DTBPB
2.5 Kg/cm2
110%
13 % Max
10%
1.5 min
45%
10%
3
Silicone Foam
0.5 Kg/cm2
50 % min
10% max
5% max
0.5  kg/cm min
50%
5% max
4
PU Foam to MMDTS19020
0.6 Kg/cm2
45% min
25% max
5% max
0.1 kg/cm min
35% min
10% max

## Some more tables ..

## Conclusions Drawn from Comparison

PU Foam to CG-04:
1. It is light weight and has good physical and comfort properties.
2. The fire resistant properties are not good as its toxicity is found to be around 2.5 and it does not meet HRR requirements.
DTBPB:
1. It has good fire resistant properties and physical properties are reasonable.
2. It loses comfort index with time and acquires permanent set.
Silicone Foam:
1. It has best fire resistance amongst available options and has good physical properties except for density which is quite high compared to other options.
2. The comfort related properties are very good and it has maximum warranty.
PU Foam to MMDTS19020:
1. It has good physical and comfort properties.
2. It meets the requirements of EN45545 in FST properties.
It is seen that none of the options is an ideal one and an optimal solution needs to be arrived

## Main Issues Raised in Complaints and on Social Media..1
A large number of complaints have been received against adoption of PU Foam as a Cushioning Material. The important points highlighted are:
1.Toxicity values of PU foam complying to EN45545 are very high when measured as per NCD 1409 standard indicating dilution in acceptable toxicity values. This will compromise passenger safety.
2.EN45545 standard includes analysis of only 8 gases against 14 in NCD1409.The gases left out are highly toxic and found in combustion products of PU foam.
3.FST properties are not included in acceptance test which is in contravention to High Power Committee recommendations appointed in the case filed in Hon’ble Supreme Court.
4.Resistance to spread of flame, deterioration in visibility due to smoke and limiting oxygen index are not included for testing to qualify a product, though these are important parameters and included in UIC564-2.
5.Deterioration in thickness and hardness up to 20% and 30% in reserved and unreserved coaches has been allowed during warranty period which is in total contradiction to test values given in specification.
6.PU foam with toxicity up to 2.5 was not being allowed, however , value of 7.27 is obtained for PU foam complying to EN45545;how can this be allowed.

## Main Issues Raised in Complaints and on Social Media….2
7. Why has this material been allowed without any trial even though all other materials have been tried out extensively before adoption.
8. Why finance is not consulted while adopting this item when it was consulted for Silicon foam.
9. A person can survive for 30 min if toxicity is less than 1, Will he survive for 5 min if toxicity is more than 7.
10. Europen trains have less capacity, are not overcrowded and are ay trains; is it prudent to adopt their lenient standard on IR with entirely different conditions.
11. Is it prudent to adopt EN45545-2 without adopting part 3,4 and 6.
12. Indian Railways in their submission to Hon’ble Supreme Court in WP178 of 2014 submitted for toxicity limit of 1 as per NCD .With new material it is more than 7, doesn’t it contradict to the submission made.
13. ISO 13571-Life threatening components of fire includes formaldehyde and acrylonitrile for measurement which are produced with PU foam but these gases are left out in EN45545.



## Methodology to be followed
### Methodology Suggested by Railway Board: 
Railway Board suggested methodology is-
- To study all available cushion materials and its specifications including various references received and issued from Board.
- To draw random samples of materials being used in Railway Coaches as on date and getting it tested in reputed neutral labs and to examine its status vis-à-vis present specification.
- To call for inputs as deemed fit from Zonal Railways.

The testing alone needs about 4 weeks time. The test reports need to be evaluated , compared and field performance to be taken into account. We therefore request for extension of tenure of the committee b three months.






# old ppt now IR : 2000-2010

+ kjgkjg
+ hgjk

## Markdown Elements (1)  error on following blank line
*italic*, **bold**, --strikeout--, super! ~subscript~, ^superscript^, [small caps]{.smallcaps}, `verbatim`

<br>

1. Ordered list item 1
2. Ordered list item 2

* Unordered list item 1
* Unordered list item 2

## Markdown Elements (2)
<!-- Visit [Appsilon](https://appsilon.com/) for more  --->

<br>

> Appsilon builds the world’s most advanced enterprise R Shiny applications, with a specialization in enterprise Shiny dashboards.
<br>

$$ u = \frac{-b \pm \sqrt[]{b^2 - 4ac}}{2a} $$


## Image
<!-- ![Image 1 - A dog](https://images.unsplash.com/photo-1643644323421-7e1cfbb2f26d?ixlib=rb-1.2.1&ixid=MnwxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHx8&auto=format&fit=crop&w=2070&q=80)
--->

## Table
     species    sepal.length    sepal.width
------------    -------------   ------------
     setosa     5.1             3.5
  virginica     7.4             2.8
 versicolor     6.4             3.2

## Multi-column Layout
:::::::::::::: {.columns}
::: {.column}
This is the **first** column

- List item 1
- List item 2
:::
::: {.column}
And this is the *second* column

* Item
* Item
:::
::::::::::::::







## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

