---
title: "**RDSO Vendor Directory Items**"
subtitle: "As on `r format(Sys.time(), '%d %B, %Y')` "
#author: ""  # "Compiled by QAM RDSO"
date: "`r format(Sys.time(), '%d %B, %Y')`" # escape " but not `r format(Sys.time(), "%I:%M")`  or "`r Sys.Date()`"
always_allow_html: true
output: 
  bookdown::pdf_document2:
    keep_tex: yes
    latex_engine: xelatex
    toc: false
#    geometry: margin=0.2in
#    fontsize: 11pt
#  word_document

Comment: >
      kable_styling(latex_options = c("striped", "scale_down"))  # scale down to fit to page
      kable_styling(latex_options = c("repeat_header")) # with longtable = T options
---

<!--  was not required \usepackage{pdflscape} -->
<!--  install.packages('tinytex')  -->
<!--  tinytex::install_tinytex() # uninstall  tinytex::uninstall_tinytex() -->


```{r setup, include=TRUE, eval=TRUE, message=FALSE, echo=FALSE, cache= TRUE}
# Set up data connection with google
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
packages <- c("tidyverse", "lubridate", "cowplot", "ggpubr", "scales", "stringr",  
              "summarytools",  "here", "googledrive" , "googlesheets", 
              "knitr",  "kableExtra",  "readxl", "writexl", "alluvial", "ggalluvial")
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) { install.packages(packages[!installed_packages]) }

lapply(packages, library, character.only = TRUE) %>% invisible()

## options(kableExtra.auto_format = FALSE) # disable globle default
options(knitr.table.format = "latex")
#library(formattable)   

library(googledrive)
library(googlesheets4)
#drive_user()  # user authorised
# drive_auth()  # authorise user

ss = "1FlEhwZ3Yn-lEs7Xb5qQXAlRQaqcQaKipK-XGU7wrHhg"
#sheet = "MasterListApril2020"  #"AllVendorRegister488"
sheet = "oldList31march20"
MasterList <- read_sheet(  ss,  sheet, skip = 2, na = "NA", col_names = TRUE,  
                          trim_ws = TRUE, .name_repair = "unique" 
                         )  #rowid_to_column()

RDSOmarch31 <- MasterList

```



```{r error2, include=FALSE, eval=FALSE, message=FALSE, echo=FALSE}

#mutate( DateApplication = parsedate::parse_date(DateApplication)) %>% 
#    mutate(qtr = paste0( substring(year(DateApplication),1,4) ,   "/Q", 
#                         quarter(DateApplication,  with_year = FALSE, fiscal_start = 4) )  )

#parse_date(dates,  approx = TRUE, default_tz = "UTC")

library(janitor)


# Cross tabulation with tabyl

RDSOmarch31 <- MasterList

#RDSOmarch31%>%  
   # mutate( DateApplication = parsedate::parse_date(DateApplication)) %>% 
   #x mutate( DateApplication = excel_numeric_to_date(DateApplication, include_time = TRUE)  ) %>%
   # mutate(qtr = paste0(substring(year(DateApplication),1,4),"/Q",quarter(DateApplication, with_year = FALSE))) %>%   #, fiscal_start = 4
#    janitor::tabyl(Directorate) %>%
#    adorn_totals(c("row", "col")) %>%    # Add totals row, column, or both.
    #adorn_ns() %>%
    #adorn_title("combined") %>%   #adorn_title(): add a title to a tabyl (or other data.frame).
    #adorn_percentages(rounding = "half up", digits = 0) %>%  # % along either axis or over the entire tabyl
    #adorn_pct_formatting(digits = 2) %>%   
    #adorn_ns() %>%  #Adornments options to control axes, rounding, and relevant formatting choices 
#    View()


# also good for tibbles !! 
# mtcars %>% adorn_totals(c("row", "col")) #%>% adorn_percentages("col")


month_levels <- c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec")
#y2 <- parse_factor(x2, levels = month_levels)    # gives waening but factor() does not
# factor(x1)  # make factores in alphabatical order
# f1 <- factor(x1, levels = unique(x1))
# f2 <- x1 %>% factor() %>% fct_inorder()

RDSOmarch31 %>% count()
RDSOmarch31 %>% count(  Less3Vendor )
RDSOmarch31 %>% count(  Less3Vendor & (as.numeric(`AA Value in Crores`) > 2) )

RDSOmarch31

RDSOmarch31 %>% filter(!is.na(`RlyBd Del List SN`) ) %>%   
                 replace_na(  list(StatusMarch31 = "Under Process") )  %>%
                  mutate( fct_infreq(`RlyBd Del List SN`) ) %>%
              # mutate(    fct_infreq(StatusMarch31)   ) %>%
                mutate(StatusMarch31 = fct_lump(StatusMarch31, n = 2)) %>%
               count(StatusMarch31)
              # mutate( Business = as.double(`AA Value in Crores`) ) %>% 
             # filter(!is.na(Business)) %>%
              #  group_by(Directorate) %>%


RDSOmarch31 %>%  filter(!is.na(`RlyBd Del List SN`) ) %>%
                 mutate(VDnow = if_else(StatusMarch31 ==  "Approved" , "Approved", "Awaited" ,  missing = NULL  ) ) %>% 
                 mutate(VDnow = as_factor(VDnow, levels(c("Approved", "Not Approved" ) )))  %>% 
                 View()
    


RDSOmarch31 %>%  filter(!is.na(`RlyBd Del List SN`) ) %>% 
    mutate(VDnow = ifelse(StatusMarch31 == "Under Process", StatusMarch31, StatusMarch31 ) ) %>% 
    mutate( StatusMarch31 = as.factor(StatusMarch31) ) %>%
    group_by(Directorate, StatusMarch31) %>% count() %>%
    spread(StatusMarch31, n)           
    

RDSOmarch31 %>% mutate( Business = as.double(`AA Value in Crores`)   )  %>%
                mutate(  LessVendors = if_else(Vendors < 3 , "Less", "OK")   )  %>%
                select( -SN, -UID, -Item, -`RlyBd Del List SN`, -`Remarks ( if critically required, else avoid)`,
                        -`PL Number`, -Less3Vendor, -`Cat I-II-III`, -`AA Value in Crores`)  %>% 
                mutate( Less2cr = if_else(Business < 2, "Less2Crores", "BusinessOver2Cr", missing = "Not Available")  ) ->  vlist


vlist %>% count(LessVendors)

```

<!--- ############################################################ --->

# The RDSO controlled items

## Description of the items and purpose

This summary analysis is based on the data provided by the respective directorates.
In case of any difference, the concerned directorate is requested to update the Google sheet, by the nominated persona who have already been provided access to edit.
This data used was accessed on  <!---`r Sys.Date()` and at time ---> `r format(Sys.time(), '%d %B, %Y')`


# Matrix of RDSO controlled items - Deletion, Merging, Continuing RDSO items

> The brakeup of the earstwhile 639 RDSO controlled items presented on the basis of items propossed for deletion by RDSO , Approved by, Board, Expected soon, under process etc.

```{r RDSOfinalstatus, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE, include=TRUE}
options(knitr.kable.NA = '')

# Status on march 31 
RDSOmarch31 %>% # mutate(VDnow = ifelse(StatusMarch31 == "Approved"|StatusMarch31 == "Merged" ,                            "Deleted", "RDSOitem"    ) ) %>%
                    group_by(Directorate, StatusMarch31) %>% count() %>%
                    spread(StatusMarch31, n)            %>% 
                kable( "latex", longtable = F, booktabs = T, 
                caption = "Items deleted, Merged, Continueing RDSO items, etc"   )   %>%
                kable_styling("striped", "hold_position", full_width = F) %>%
                kable_styling(latex_options = "striped")                  %>%
                kable_styling(latex_options = c("scale_down"))            %>%
                kable_styling(font_size = 10)   %>%
                kable_styling(latex_options = c("repeat_header"))         %>%
                    column_spec(1, width = "15em") %>%                    #SN
                    column_spec(2, width = "8em") %>%                     # Directorate
                    column_spec(3, width = "8em") %>%
                    column_spec(4, width = "8em") %>%
                    column_spec(5, width = "12em") %>%
                    column_spec(6, width = "5em") %>%
                    column_spec(7, width = "6em")  #%>%     column_spec(8, width = "12em") 
```

Total items after deletion of items approved by Railway Board :
 `r  RDSOmarch31 %>% filter(!StatusMarch31 =="Approved" | is.na(StatusMarch31) ) %>% count() ` 
 
Total items after deletion of items approved by Railway Board and Merging of similar items :
 `r  RDSOmarch31 %>% filter(  !(StatusMarch31 =="Approved"|StatusMarch31 =="Merged" )| is.na(StatusMarch31)  )  %>% count() ` 


<!--- ################################################################ --->
&nbsp; 

\pagebreak

# Items with less than three vendors

## After addition of vendors and deletions of items approved by board 

The table of items with less than three vendors after ignoring the items already approved by Railway Board.


```{r lessthan3vendor, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE, include=TRUE}

# items break up of less than three items :
RDSOmarch31 %>%     filter(Vendors  < 3)   %>%
                    filter(!StatusMarch31 =="Approved" | is.na(StatusMarch31) )  %>% 
                    group_by(Directorate,  Less3Vendor) %>%  
                    count(Less3Vendor )  %>%
                    spread(Less3Vendor, n)   %>%
                kable( "latex",  booktabs = T, longtable = T,
                caption = "Table of items with less than three vendors"  )   %>%
                kable_styling(latex_options = "striped")                %>%
                kable_styling(latex_options = c("scale_down")    )      %>%
                kable_styling(latex_options = c("repeat_header") )      %>%
                    column_spec(1, width = "12em") %>%              
                    column_spec(2, width = "8em") %>%              
                    column_spec(3, width = "8em") %>%
                    column_spec(4, width = "8em") %>%
                    column_spec(5, width = "12em") 
```



**Total item with less than three vendors:**  `r  RDSOmarch31 %>% filter(Vendors  < 3)   %>%
                                               filter(!StatusMarch31 =="Approved" | is.na(StatusMarch31) )  %>%  count() ` 


## RDSO rationalisation / Merging of items 

RDSO has rationalised items based on the similiarity of specs/STR/industry.

The list of items is as below:

```{r RDSOmergedlist, eval=TRUE, include=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
RDSOmarch31 %>%     select(SN, Directorate, UID, Item, Vendors, StatusMarch31  )   %>% 
                    mutate(Item = ifelse(str_length(Item) < 40, Item, 
                               paste0( str_sub(Item, 1, 40)   , " ...." ) )  )   %>%
                    filter(StatusMarch31 == "Merged"  )                         %>%
                    mutate(tickno = 1, SN = cumsum(tickno)   )   %>% 
                    select(-StatusMarch31, -tickno)                            %>%
                    kable( "latex", longtable = T, booktabs = T, 
                    caption = "Items Rationalised/Merged"   )                   %>%
                    kable_styling(latex_options = c("scale_down"))              %>%
                    kable_styling(latex_options = c("repeat_header"))           %>%
             #   kable_styling(latex_options = "striped")                       %>%
                    column_spec(1, width = "3em")  %>%              #SN
                    column_spec(2, width = "5em") %>%              # Directorate
                    column_spec(3, width = "5em") %>%
                    column_spec(4, width = "25em") %>%
                    column_spec(5, width = "3em") %>%
                    column_spec(6, width = "5em") %>%
                    column_spec(7, width = "6em") 
       # collapse_rows(columns = 2, valign = "top", row_group_label_position = 'stack') 
       # collapse_rows(1:2, row_group_label_position = 'stack') %>%
                
```

 
## Final Table of items with less than three vendors 

Final Table of items with less than three vendors after `deletion of items by Railway board`,  `rationalisation of items by RDSO` and `additon of new vendors by RDSO`.

```{r finallessthan3vendor1, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE, include=TRUE}

# items break up of less than three items :
RDSOmarch31 %>%     filter(Vendors  < 3)   %>%
                    filter(!(StatusMarch31 =="Approved" | StatusMarch31 =="Merged")| is.na(StatusMarch31) )  %>% 
                   # filter(!StatusMarch31 =="Merged")  %>%
                    group_by(Directorate,  Less3Vendor) %>%  
                    count(Less3Vendor )  %>%
                    spread(Less3Vendor, n)   %>%
                kable( "latex",  booktabs = T, longtable = T,
                caption = "Table of items with less than three vendors"  )   %>%
                kable_styling(latex_options = "striped")                %>%
                kable_styling(latex_options = c("scale_down")    )      %>%
                kable_styling(latex_options = c("repeat_header") )      %>%
                    column_spec(1, width = "12em") %>%              
                    column_spec(2, width = "8em") %>%              
                    column_spec(3, width = "8em") %>%
                    column_spec(4, width = "8em") %>%
                    column_spec(5, width = "12em") 
```


 
 
## The final list of items with less than three vendors

The list of items with less than three vendors after deletion of item by Board and Rationalisation by RDSOO.

```{r RDSOless3vendorprint1, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE, include=TRUE}

## check up variables before print

RDSOmarch31 %>%     filter(Vendors  < 3)   %>%
                    filter(!(StatusMarch31 =="Approved" | StatusMarch31 =="Merged")| is.na(StatusMarch31)                              )  %>% 
                    select(SN, Directorate, UID, Item, Vendors,`AA Value in Crores`, 
                       `RlyBd Del List SN`, StatusMarch31  )                     %>% 
                    mutate(Item = ifelse(str_length(Item) < 40, Item, 
                                          paste0( str_sub(Item, 1, 40) , " ...." ) )  )   %>%
                    mutate(tickno = 1, SN = cumsum(tickno)   )   %>% 
                    mutate(`AA Value in Crores`= ifelse(is.na(`AA Value in Crores`), 
                                                        "NAvl", `AA Value in Crores` ) )   %>% 
                    select(-tickno, -StatusMarch31,  -`RlyBd Del List SN`)                   %>%
                    kable( "latex", longtable = T, booktabs = T, 
                    caption = "List of  items with less than 3 Vendors"   )     %>%
                    kable_styling(latex_options = c("scale_down"))              %>%
                    kable_styling(latex_options = c("repeat_header"))           %>%
             #   kable_styling(latex_options = "striped")                       %>%
                    column_spec(1, width = "3em")  %>%              #SN
                    column_spec(2, width = "5em") %>%              # Directorate
                    column_spec(3, width = "5em") %>%
                    column_spec(4, width = "25em") %>%
                    column_spec(5, width = "3em") %>%
                    column_spec(6, width = "5em") %>%
                    column_spec(7, width = "6em") %>%
                    column_spec(8, width = "10em") 
       # collapse_rows(columns = 2, valign = "top",row_group_label_position = 'stack') 
       # collapse_rows(1:2, row_group_label_position = 'stack') %>%
                


```








&nbsp; 

\pagebreak

# The complete Master data of 639 items 

The data includes those item deleted or merged with other similar items

```{r RDSOmasterprint, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE, include=TRUE}

## check up variables before print

RDSOmarch31 %>% select(SN, Directorate, UID, Item, Vendors,`AA Value in Crores`, 
                       `RlyBd Del List SN`, StatusMarch31  )  %>% 
                kable( "latex", longtable = T, booktabs = T, 
                caption = "Table of RDSO Vendor Directory items"   )   %>%
                kable_styling(latex_options = c("scale_down"))         %>%
                kable_styling(latex_options = c("repeat_header"))      %>%
             #   kable_styling(latex_options = "striped")               %>%
                    column_spec(1, width = "3em") %>%              #SN
                    column_spec(2, width = "5em") %>%              # Directorate
                    column_spec(3, width = "5em") %>%
                    column_spec(4, width = "25em") %>%
                    column_spec(5, width = "3em") %>%
                    column_spec(6, width = "5em") %>%
                    column_spec(7, width = "6em") %>%
                    column_spec(8, width = "10em")  %>% landscape()
       # collapse_rows(columns = 2, valign = "top",row_group_label_position = 'stack') 
       # collapse_rows(1:2, row_group_label_position = 'stack') %>%
                


```


```{r venderlist, eval=FALSE, echo=FALSE, message=FALSE, warning=FALSE, include=TRUE}
## check up variables before print
RDSOvd <-  gs_read(ss = allvendorhandle, ws = 2 , skip = 2, col_names = FALSE,verbose = TRUE)    # %>% rowid_to_column()
# suppressMessages(expr)
RDSOvd %<>% rename(SN = X1)

RDSOvd %>% filter(grepl("QA", X3))  -> RDSOvd2
RDSOvd2  %>%   mutate( QAD = as_factor(X2) , SN = as.numeric(SN) )       %>%    
               mutate( QA = fct_collapse(QAD, 
                   QAM = c("Carriage", "MP", "M&C Dte", "wagon", "Wagon"),
                   QAC = c("B&S", "Works", "QAC/Track Design-II", "TMM Dte.",  
                           "Track Design", "Track Design I", "Track Design II", 
                           "Track Design", "Track Design I", "QAC/Track Design-II"),
                   QST = c("QA/S&T", "SIG" , "Telecom" ),  
                   QElect = c("TI")  )                  )   %>% 
    select( SN, QAD= X3, Item = X2, X3, Vendors = X4,X5,X6, X7,  X9)   %>%
    arrange(SN) %>% filter( !is.na(SN) ) %>%
    kable( "latex", longtable = T, booktabs = T, 
    caption = "Table of RDSO Vendor Directory items"   )   %>%
    kable_styling(latex_options = c("scale_down"))         %>%
   # add_header_above(c(" ", "Group 1" = 5, "Group 2" = 6)) %>%
    kable_styling(latex_options = c("repeat_header"))      %>%
        column_spec(1, width = "3em") %>%
        column_spec(2, width = "5em") %>%
        column_spec(3, width = "20em") %>%
        column_spec(4, width = "6em") %>%
        column_spec(5, width = "4em") %>%
        column_spec(6, width = "4em") %>%
        column_spec(7, width = "4em") %>%
        column_spec(8, width = "6em") %>%
        column_spec(9, width = "4em") %>%
        column_spec(10, width = "4em") %>%
        column_spec(11, width = "4em") %>%
        column_spec(12, width = "4em") %>%
       # collapse_rows(columns = 2, valign = "top",row_group_label_position = 'stack') 
       # collapse_rows(1:2, row_group_label_position = 'stack') %>%
    landscape()
```



# Annexure 






```{r RDSOeuler, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
library(eulerr)
set.seed(1)

#plot(venn(RDSOmarch31[, 4:6]))
A = 1
B = 2
s2 <- c(A , B )
# plot(s2) # do not plot


#RDSOmarch31
gkeuler <- c("A" = 15, "B" = 15, "C" = 3,
                                "A&B" = 3, "A&C" = 0, "B&C" = 0,
                                "A&B&C" = 3)
completely_contained <- euler(gkeuler)
plot(completely_contained,
    # labels = list(col = c("white", "black", "black") ),
     labels = c("To m  ggg", "Greg", "Albe \n rta" ),
     edges = list(col = "white", lex = 2),
     fills = c("magenta", "cyan", "yellow"))   # orange


#plot(venn(s2))
#plot(eulerr::euler(s2), quantities = TRUE)

#plot(eulerr::euler(RDSOmarch31), quantities = TRUE)

```

