---
title: "RDSO Vendor Directory"
subtitle: "Total items 638"
author: "PED/QAM/RDSO"
date: "`r format(Sys.time(), '%d %B, %Y')`" # " needs escape but not `r format(Sys.time(), "%I:%M")`  or "`r Sys.Date()`"
output: 
  bookdown::pdf_document2:
    keep_tex: yes
    latex_engine: xelatex
    toc: true
Comment: >
    This comment in YAML is also too long
    and newlines survive from parsing!
---

# Initial setup of the book

We can include details.

<!--  comment : needs  latex_engine: xelatex and also output settings near knit button -->
<!--  was not required \usepackage{pdflscape} -->
<!--  install.packages('tinytex')  -->
<!--  tinytex::install_tinytex() # uninstall  tinytex::uninstall_tinytex() -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
## RDSO Vendor Analysis  #########################
library(tidyverse)
packages <- c("tidyverse", "lubridate", "cowplot", "ggpubr", "scales", "stringr",  
              "summarytools",  "here", "googlesheets", 
              "knitr",  "kableExtra")
# if not Instaled 
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) { install.packages(packages[!installed_packages]) }

lapply(packages, library, character.only = TRUE) %>% invisible()
library(googlesheets)   
allvendorhandle   <-   gs_title("RDSO MASTERLIST VENDOR DATA 26 Jan")      # gs by title

```

## R Markdown

see  <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. 

```{r,  echo=TRUE}

library(knitr)
library(kableExtra)
dt <- mtcars[1:5, 1:6]
kable(dt, "latex", booktabs = T) %>%
kable_styling(latex_options = "striped")
```


# styling

```{r,  echo=TRUE}
dt <- mtcars[1:5, 1:6]
kable(cbind(dt, dt, dt), "latex", booktabs = T) %>%
kable_styling(latex_options = c("striped", "scale_down"))
```



# The chilld files joining

```{r, child=c('one.Rmd', 'two.Rmd', 'three.Rmd' )}
```



You can embed an R code chunk like this:

```{r cars, include=TRUE, message=FALSE, echo=FALSE}
RDSOvd <-  gs_read(ss = allvendorhandle, ws = 2 , skip = 2, col_names = FALSE,verbose = TRUE)    # %>% rowid_to_column()
# suppressMessages(expr)
RDSOvd %<>% rename(SN = X1)

RDSOvd %>% filter(grepl("QA", X3))  -> RDSOvd2

RDSOvd2 %>% 
    kable( "latex", longtable = T, booktabs = T, 
    caption = "Longtable of Vendor Directory")           %>%
    add_header_above(c(" ", "Group 1" = 5, "Group 2" = 6)) %>%
    kable_styling(latex_options = c( "repeat_header"), full_width = F)      %>%
    kable_styling(font_size = 7)      %>%
        column_spec(1, width = "3em") %>%
        column_spec(2, bold = T, color = "red", width = "12em") %>%
        column_spec(3, width = "4em") %>%
        column_spec(4, width = "4em") %>%
        column_spec(5, width = "4em") %>%
        column_spec(6, width = "4em") %>%
        column_spec(7, width = "4em") %>%
        column_spec(8, width = "6em") %>%
        column_spec(9, width = "4em") %>%
        column_spec(10, width = "4em") %>%
        column_spec(11, width = "4em") %>%
        column_spec(12, width = "4em") %>%
        row_spec(0, angle = 45)  %>%
        row_spec(1, strikeout = T)     %>%
        row_spec(5:6, bold = T, color = "white", background = "black") %>%
        landscape()

```

## Including Plots




>    kable_styling(latex_options = c("striped", "scale_down")) %>%
>    kable_styling(latex_options = "striped", stripe_index = c(1,2, 5:6))     %>%



```{r pressure, echo=FALSE}

RDSOvd2 %>%  kable( "latex", longtable = T, booktabs = T, 
    caption = "Table of Civil Vendor Directory items")     %>%
    kable_styling(latex_options = c("scale_down")) %>%
    add_header_above(c(" ", "Group 1" = 5, "Group 2" = 6)) %>%
    kable_styling(latex_options = c("repeat_header"))      %>%
        column_spec(1, width = "3em") %>%
        column_spec(2, width = "12em") %>%
        column_spec(3, width = "4em") %>%
        column_spec(4, width = "4em") %>%
        column_spec(5, width = "4em") %>%
        column_spec(6, width = "4em") %>%
        column_spec(7, width = "4em") %>%
        column_spec(8, width = "6em") %>%
        column_spec(9, width = "4em") %>%
        column_spec(10, width = "4em") %>%
        column_spec(11, width = "4em") %>%
        column_spec(12, width = "4em") %>%

    landscape()

#plot(pressure)
# dat = dat %>% mutate(candy.flag = factor(ifelse(var == "Candy", "Candy", "Non-Candy")))

# dat <- as_data_frame(c("Candy","Sanitizer","Candy","Water","Cake","Candy","IceCream","Gum","Candy","Coffee"))
# colnames(dat) <- "var"
# dat %>% mutate(var = replace(var, var != "Candy", "Not Candy"))  # faster
#

```




Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
