---
title: "RDSO Vendor Directory"
subtitle: "Total items 638"
author: "QAM/RDSO"
date: "`r format(Sys.time(), '%d %B, %Y')`" # escape " but not `r format(Sys.time(), "%I:%M")`  or "`r Sys.Date()`"
always_allow_html: true
output: 
  bookdown::pdf_document2:
    keep_tex: yes
    latex_engine: xelatex
    toc: true
#    geometry: margin=0.2in
#    fontsize: 11pt
  html_document:
    toc: true
    toc_depth: 2  #the default is 3
    theme: readable
    highlight: pygments
    code_folding: hide
    keep_md: true
Comment: >
    This comment in YAML is also too long
    and newlines survive from parsing!
    theme  "default", "cerulean", "journal", "flatly", "readable", "spacelab", "united",      "cosmo", "lumen", "paper", "sandstone", "simplex", and "yeti".
     highlight for  syntax style  "default", "tango", "pygments", "kate", "monochrome",        "espresso", "zenburn", "haddock", and "textmate".
    All docs by rmarkdown::render("my-document.Rmd", output_format = "all"). learn ender
    Better to do your initial work in an R script and do source("gun-deaths.R")
     against rmarkdown::render() function 

     run scripts directly from the shell using Rscript: "Rscript gun-deaths.R" 
     and markdown shell for Rmd Rscript -e "rmarkdown::render('gun-deaths.Rmd')"
     for tables compile may set  :options(knitr.table.format = "latex") 
     but now automatically done options(kableExtra.auto_format = FALSE)
     recommended to load this package entirely via library(kableExtra) in main doc 
---

# Initial setup of the book

I need to add the following
# header-includes:

<!---
    - \usepackage{booktabs}
    - \usepackage{longtable}
    - \usepackage{array}
    - \usepackage{multirow}
    - \usepackage{wrapfig}
    - \usepackage{float}
    - \usepackage{colortbl}
    - \usepackage{pdflscape}
    - \usepackage{tabu}
    - \usepackage{threeparttable}
    - \usepackage{threeparttablex}
    - \usepackage[normalem]{ulem}
    - \usepackage{makecell}
    - \usepackage{xcolor}

   # header-includes:
        - \usepackage{booktabs}
        - \usepackage{longtable}
        - \usepackage{array}
        - \usepackage{multirow}
        - \usepackage{wrapfig}
        - \usepackage{float}
        - \usepackage{colortbl}
        - \usepackage{pdflscape}
        - \usepackage{tabu}
        - \usepackage{threeparttable}
        - \usepackage{threeparttablex}
        - \usepackage[normalem]{ulem}
        - \usepackage{makecell}
        - \usepackage{xcolor}
--->

We can include details.

Printed : `r Sys.time()` on `r Sys.Date()` and formated date `r format(Sys.time(), '%d %B, %Y')`


<!--  comment : needs  latex_engine: xelatex and also output settings near knit button -->
<!--  was not required \usepackage{pdflscape} -->
<!--  install.packages('tinytex')  -->
<!--  tinytex::install_tinytex() # uninstall  tinytex::uninstall_tinytex() -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
## RDSO Vendor Analysis  #########################
library(tidyverse)
packages <- c("tidyverse", "lubridate", "cowplot", "ggpubr", "scales", "stringr",  
              "summarytools",  "here", "googlesheets", 
              "knitr",  "kableExtra")
# if not Instaled 
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) { install.packages(packages[!installed_packages]) }

lapply(packages, library, character.only = TRUE) %>% invisible()

library(formattable) # for pretty html tables

library(googlesheets)   
allvendorhandle   <-   gs_title("RDSO MASTERLIST VENDOR DATA 26 Jan")      # gs by title

# filter your data to use youth <- gun_deaths %>% filter(age <= 65)

kable(mtcars, "latex", booktabs = T) %>%
    kable_styling(latex_options = "striped")


```

<!--- why comment errored ? We have data about r nrow (gun_deaths) individuals killed by guns. Only "`text nrow(gun_deaths) - nrow(youth)`" are older than 65. The distribution of the remainder is shown below: 

You can also knit this programmatically from the console by running the command
rmarkdown::render("example.Rmd")
--->


## RDSO vendor directory 

<!---
see  <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. 

```{r,  echo=TRUE}

library(knitr)
library(kableExtra)
library(formattable) # for pretty html tables

dt <- mtcars[1:5, 1:6]
kable(dt, "latex", booktabs = T) %>%
kable_styling(latex_options = "striped")
```


# styling

```{r,  echo=TRUE}
dt <- mtcars[1:5, 1:6]
kable(cbind(dt, dt, dt), "latex", booktabs = T) %>%
kable_styling(latex_options = c("striped", "scale_down"))
```

--->
# The chilld files joining

```{r, child=c('one.Rmd', 'two.Rmd', 'three.Rmd' ) }

```

<!--- Remarks
```{r, child=c('three.Rmd' )}
```

--->



You can embed an R code chunk like this:
but it is actual work



```{r venderlist, include=TRUE, message=FALSE, echo=TRUE}
RDSOvd <-  gs_read(ss = allvendorhandle, ws = 2 , skip = 2, col_names = FALSE,verbose = TRUE)    # %>% rowid_to_column()
# suppressMessages(expr)
RDSOvd %<>% rename(SN = X1)

RDSOvd %>% filter(grepl("QA", X3))  -> RDSOvd2

RDSOvd2 %>% head() %>%
    kable( "latex", longtable = T, booktabs = T, 
           caption = "Longtable of Vendor Directory"         )           %>%
    add_header_above(c(" ", "Group 1" = 5, "Group 2" = 6))                %>%
    kable_styling(latex_options = c( "repeat_header"), full_width = F)      %>%
    kable_styling(font_size = 7)      %>%
        column_spec(1, width = "3em") %>%
        column_spec(2, bold = T, color = "red", width = "12em") %>%
        column_spec(3, width = "4em") %>%
        column_spec(4, width = "4em") %>%
        column_spec(5, width = "4em") %>%
        column_spec(6, width = "4em") %>%
        column_spec(7, width = "4em") %>%
        column_spec(8, width = "6em") %>%
        column_spec(9, width = "4em") %>%
        column_spec(10, width = "4em") %>%
        column_spec(11, width = "4em") %>%
        column_spec(12, width = "4em") %>%
        row_spec(0, angle = 45)  %>%
        row_spec(1, strikeout = T)     %>%
        row_spec(5:6, bold = T, color = "white", background = "black") %>%
        # collapse_rows(1:3, row_group_label_position = 'stack')  %>%
        landscape()

```


##  Try improved table

```{r test2, include=TRUE, message=FALSE, echo=TRUE}
collapse_rows_dt <- expand.grid(
                        Country = sprintf('Country with a long name %s', c('A', 'B')),
                        State = sprintf('State %s', c('a', 'b')),
                        City = sprintf('City %s', c('1', '2')),
                        District = sprintf('District %s', c('1', '2')) ) %>% 
                    arrange(Country, State, City) %>%
                    mutate_all(as.character) %>%
                    mutate(C1 = rnorm(n()), C2 = rnorm(n()) )

kable(collapse_rows_dt, "latex", longtable = T, booktabs = T, align = "c", linesep = '') %>%
                    collapse_rows(1:3, row_group_label_position = 'stack')
```

testing above

```{r venderlist6, include=TRUE, message=FALSE, echo=FALSE}
#RDSOvd <-  gs_read(ss = allvendorhandle, ws = 2 , skip = 2, col_names = FALSE,verbose = TRUE)    # %>% rowid_to_column()
# suppressMessages(expr)
#RDSOvd %<>% rename(SN = X1)
#RDSOvd %>% filter(grepl("QA", X3))  -> RDSOvd2
#? RDSOvd3 <- RDSOvd %>% select(-X1)
#RDSOvdlined <- RDSOvd %>% #           arrange(SN) %>%mutate_all(as.character) 

#? kable(RDSOvd3, "latex", longtable = T, booktabs = T, align = "c", linesep = '') %>%  collapse_rows(1:12)


```


RDSOvdlined %>%
    kable( "latex", longtable = T, booktabs = T, 
    caption = "Longtable of Vendor Directory")           %>%
    add_header_above(c(" ", "Group 1" = 5, "Group 2" = 6)) %>%
    kable_styling(latex_options = c( "repeat_header"), full_width = F)      %>%
    kable_styling(font_size = 7)      %>%
        column_spec(1, width = "3em") %>%
        column_spec(2, bold = T, color = "red", width = "12em") %>%
        column_spec(3, width = "4em") %>%
        column_spec(4, width = "4em") %>%
        column_spec(5, width = "4em") %>%
        column_spec(6, width = "4em") %>%
        column_spec(7, width = "4em") %>%
        column_spec(8, width = "6em") %>%
        column_spec(9, width = "4em") %>%
        column_spec(10, width = "4em") %>%
        column_spec(11, width = "4em") %>%
        column_spec(12, width = "4em") %>%
        row_spec(0, angle = 45)  %>%
        row_spec(1, strikeout = T)     %>%
        row_spec(5:6, bold = T, color = "white", background = "black") %>%
        # collapse_rows(1:3, row_group_label_position = 'stack')  %>%
        landscape()




## Including Plots







>    kable_styling(latex_options = c("striped", "scale_down")) %>%
>    kable_styling(latex_options = "striped", stripe_index = c(1,2, 5:6))     %>%



```{r Vlist7, echo=TRUE}
RDSOvd2  %>%   mutate( QAD = as_factor(X2) , SN = as.numeric(SN) )       %>%    
               mutate( QA = fct_collapse(QAD, 
                   QAM = c("Carriage", "MP", "M&C Dte", "wagon", "Wagon"),
                   QAC = c("B&S", "Works", "QAC/Track Design-II", "TMM Dte.",  
                           "Track Design", "Track Design I", "Track Design II", 
                           "Track Design", "Track Design I", "QAC/Track Design-II"),
                   QST = c("QA/S&T", "SIG" , "Telecom" ),  
                   QElect = c("TI")  )                  )   %>% 
    select( SN, QAD= X3, Item = X2, X3, Vendors = X4,X5,X6, X7,  X9)   %>%
    arrange(SN) %>% filter( !is.na(SN) ) %>%
    kable( "latex", longtable = T, booktabs = T, 
    caption = "Table of RDSO Vendor Directory items"   )   %>%
    kable_styling(latex_options = c("scale_down"))         %>%
   # add_header_above(c(" ", "Group 1" = 5, "Group 2" = 6)) %>%
    kable_styling(latex_options = c("repeat_header"))      %>%
        column_spec(1, width = "3em") %>%
        column_spec(2, width = "5em") %>%
        column_spec(3, width = "20em") %>%
        column_spec(4, width = "6em") %>%
        column_spec(5, width = "4em") %>%
        column_spec(6, width = "4em") %>%
        column_spec(7, width = "4em") %>%
        column_spec(8, width = "6em") %>%
        column_spec(9, width = "4em") %>%
        column_spec(10, width = "4em") %>%
        column_spec(11, width = "4em") %>%
        column_spec(12, width = "4em") %>%
       # collapse_rows(columns = 2, valign = "top",row_group_label_position = 'stack') %>%
    landscape()

```


#plot(pressure)
# dat = dat %>% mutate(candy.flag = factor(ifelse(var == "Candy", "Candy", "Non-Candy")))

# dat <- as_data_frame(c("Candy","Sanitizer","Candy","Water","Cake","Candy","IceCream","Gum","Candy","Coffee"))
# colnames(dat) <- "var"
# dat %>% mutate(var = replace(var, var != "Candy", "Not Candy"))  # faster


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.


# The code below will automatically include the image in the rmarkdown document
<!---  not worked
```{r , eval=FALSE,  include=TRUE, echo=TRUE}
RDSOvd2 %>%    head()  %>%  
kable( "latex", booktabs = T) %>%
column_spec(1, bold = T)   %>% as_image()
   # kable_as_image()  # kable_as_image is deprecated instead save_kable or as_image .

```
--->

# End of doc notes
