---
title: "**RDSO Vendor Directory controlled items - Draft**"
subtitle: "( Complete current status of all the RDSO vendor directory's 639 items as on 26 Jan 2020 )"
author: "Compiled by QAM RDSO"
date: "`r format(Sys.time(), '%d %B, %Y')`" # escape " but not `r format(Sys.time(), "%I:%M")`  or "`r Sys.Date()`"
always_allow_html: true
output: 
  bookdown::pdf_document2:
    keep_tex: yes
    latex_engine: xelatex
    toc: false
#    geometry: margin=0.2in
#    fontsize: 11pt
  html_document:
    toc: true
    toc_depth: 2  #the default is 3
    theme: readable
    highlight: pygments
    code_folding: hide
    keep_md: true
    
Comment: >
    long  YAML comment and newlines survive parsing!
    theme  "default", "cerulean", "journal", "flatly", "readable", "spacelab", "united",      "cosmo", "lumen", "paper", "sandstone", "simplex", and "yeti".
     highlight for  syntax style  "default", "tango", "pygments", "kate", "monochrome",        "espresso", "zenburn", "haddock", and "textmate".
    All docs by rmarkdown::render("my-document.Rmd", output_format = "all"). learn ender
    Better to do your initial work in an R script and do source("gun-deaths.R")
     against rmarkdown::render() function 

     run scripts directly from the shell using Rscript: "Rscript gun-deaths.R" 
     and markdown shell for Rmd Rscript -e "rmarkdown::render('gun-deaths.Rmd')"
     for tables compile may set  :options(knitr.table.format = "latex") 
     but now automatically done options(kableExtra.auto_format = FALSE)
     recommended to load this package entirely via library(kableExtra) in main doc 
         header-includes:
      - \usepackage{booktabs}
      - \usepackage{longtable}
      - \usepackage{array}
      - \usepackage{multirow}
      - \usepackage{wrapfig}
      - \usepackage{float}
      - \usepackage{colortbl}
      - \usepackage{pdflscape}
      - \usepackage{tabu}
      - \usepackage{threeparttable}
      - \usepackage{threeparttablex}
      - \usepackage[normalem]{ulem}
      - \usepackage{makecell}
      - \usepackage{xcolor}
      
      kable_styling(latex_options = c("striped", "scale_down"))  # scale down to fit to page
      kable_styling(latex_options = c("repeat_header")) # to repeat header in long table
      # , longtable = T, in options of table
      
      
---

# The RDSO controlled items

## Description of the items and purpose

This vendor directory data is printed based on the Google sheet data provided by the respective directorates. In case of any difference noticed by any directorate, they are requested to verify and update the Google sheet, access to the same has already been given to the nominated persons of the respective directorates.


<!---
Date:  `r Sys.Date()` 
Formated date: `r format(Sys.time(), '%d %B, %Y')`  --->

<!--  was not required \usepackage{pdflscape} -->
<!--  install.packages('tinytex')  -->
<!--  tinytex::install_tinytex() # uninstall  tinytex::uninstall_tinytex() -->



```{r setup, include=FALSE, eval=TRUE, message=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE)
## RDSO Vendor Analysis  #########################
library(tidyverse)
packages <- c("tidyverse", "lubridate", "cowplot", "ggpubr", "scales", "stringr",  
              "summarytools",  "here", "googlesheets", 
              "knitr",  "kableExtra",
              "readxl", "writexl",
              "alluvial", "ggalluvial")
# if not Instaled 
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) { install.packages(packages[!installed_packages]) }

lapply(packages, library, character.only = TRUE) %>% invisible()

                                     ## options(kableExtra.auto_format = FALSE) # disable globle default
options(knitr.table.format = "latex")

library(formattable) # for pretty html tables

library(googlesheets)  
library(googledrive) # better  use  for files suggested by jenny bryon

# works with direct correct file name
allvendorhandle   <-   gs_title("MASTER VENDOR LIST March2020")      # gs by title

allvendorhandle
# range = "R1C1:R4C3" | "B3:F80" | cell_cols(1:4) | cell_limits(  c(1, 4), c(5, NA) | cell_rows(1:1000) )
# locale, trim_ws, na, comment, n_max
RDSOmarch31     <-   gs_read(ss = allvendorhandle,   ws = 1 , skip = 2, col_names = TRUE,verbose = TRUE) # %>% rowid_to_column()

# filter your data to use youth <- gun_deaths %>% filter(age <= 65)

# kable(mtcars, "latex", booktabs = T) %>% kable_styling(latex_options = "striped")


```


```{r RDSOfinallist, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
## check up variables before print
RDSOmarch31 %>% select(SN, Directorate, UID, Item, Vendors,`AA Value in Crores`, `RlyBd Del List SN`, StatusMarch31, Prospects) 

```


# Details of RDSO controlled items - Deletion, Merging, Continuing RDSO items

```{r RDSOfinalstatus, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE, include=TRUE}
options(knitr.kable.NA = '')
# Status on march 31 
RDSOmarch31 %>%     #mutate(VDnow = ifelse(StatusMarch31 == "Approved"|StatusMarch31 == "Merged" ,  "Deleted", "RDSOitem"    ) ) %>%
                    group_by(Directorate, StatusMarch31) %>% count() %>%
                    spread(StatusMarch31, n)            %>% 
                kable( "latex", longtable = F, booktabs = T, 
                caption = "Items deleted, Merged, Continueing RDSO items, etc"   )   %>%
                kable_styling("striped", "hold_position", full_width = F) %>%
                kable_styling(latex_options = "striped")  %>%
                kable_styling(latex_options = c("scale_down"))         %>%
                kable_styling(latex_options = c("repeat_header"))      %>%
                    column_spec(1, width = "8em") %>%              #SN
                    column_spec(2, width = "8em") %>%              # Directorate
                    column_spec(3, width = "8em") %>%
                    column_spec(4, width = "8em") %>%
                    column_spec(5, width = "8em") %>%
                    column_spec(6, width = "5em") %>%
                    column_spec(7, width = "6em") %>%
                    column_spec(8, width = "12em") 


```


&nbsp; 

\pagebreak

# Items with less then three vendors

```{r lessthen3vendor, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE, include=TRUE}

# items break up of less then three items :
RDSOmarch31 %>%     
                    group_by(Directorate,  Less3Vendor) %>%  
                    count(Less3Vendor )  %>%
                    spread(Less3Vendor, n)   %>%
                kable( "latex", longtable = T, booktabs = T, 
                caption = "Table of RDSO Vendor Directory items with less then three vendors"   )   %>%
                kable_styling(latex_options = "striped")  %>%
                kable_styling(latex_options = c("scale_down"))         %>%
                kable_styling(latex_options = c("repeat_header"))      %>%
                    column_spec(1, width = "12em") %>%              
                    column_spec(2, width = "8em") %>%              
                    column_spec(3, width = "8em") %>%
                    column_spec(4, width = "8em") %>%
                    column_spec(5, width = "12em") 



```


&nbsp; 

\pagebreak

# The complete Master data of 639 items 

The data includes those item deleted or merged with other similar items

```{r RDSOmasterprint, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE, include=TRUE}

## check up variables before print

RDSOmarch31 %>% select(SN, Directorate, UID, Item, Vendors,`AA Value in Crores`, 
                       `RlyBd Del List SN`, StatusMarch31  )  %>% 
                kable( "latex", longtable = T, booktabs = T, 
                caption = "Table of RDSO Vendor Directory items"   )   %>%
                kable_styling(latex_options = c("scale_down"))         %>%
                kable_styling(latex_options = c("repeat_header"))      %>%
             #   kable_styling(latex_options = "striped")               %>%
                    column_spec(1, width = "3em") %>%              #SN
                    column_spec(2, width = "5em") %>%              # Directorate
                    column_spec(3, width = "5em") %>%
                    column_spec(4, width = "20em") %>%
                    column_spec(5, width = "3em") %>%
                    column_spec(6, width = "5em") %>%
                    column_spec(7, width = "6em") %>%
                    column_spec(8, width = "12em")  %>% landscape()
       # collapse_rows(columns = 2, valign = "top",row_group_label_position = 'stack') 
       # collapse_rows(1:2, row_group_label_position = 'stack') %>%
                


```


```{r venderlist, eval=FALSE, echo=FALSE, message=FALSE, warning=FALSE, include=TRUE}
## check up variables before print
RDSOvd <-  gs_read(ss = allvendorhandle, ws = 2 , skip = 2, col_names = FALSE,verbose = TRUE)    # %>% rowid_to_column()
# suppressMessages(expr)
RDSOvd %<>% rename(SN = X1)

RDSOvd %>% filter(grepl("QA", X3))  -> RDSOvd2
RDSOvd2  %>%   mutate( QAD = as_factor(X2) , SN = as.numeric(SN) )       %>%    
               mutate( QA = fct_collapse(QAD, 
                   QAM = c("Carriage", "MP", "M&C Dte", "wagon", "Wagon"),
                   QAC = c("B&S", "Works", "QAC/Track Design-II", "TMM Dte.",  
                           "Track Design", "Track Design I", "Track Design II", 
                           "Track Design", "Track Design I", "QAC/Track Design-II"),
                   QST = c("QA/S&T", "SIG" , "Telecom" ),  
                   QElect = c("TI")  )                  )   %>% 
    select( SN, QAD= X3, Item = X2, X3, Vendors = X4,X5,X6, X7,  X9)   %>%
    arrange(SN) %>% filter( !is.na(SN) ) %>%
    kable( "latex", longtable = T, booktabs = T, 
    caption = "Table of RDSO Vendor Directory items"   )   %>%
    kable_styling(latex_options = c("scale_down"))         %>%
   # add_header_above(c(" ", "Group 1" = 5, "Group 2" = 6)) %>%
    kable_styling(latex_options = c("repeat_header"))      %>%
        column_spec(1, width = "3em") %>%
        column_spec(2, width = "5em") %>%
        column_spec(3, width = "20em") %>%
        column_spec(4, width = "6em") %>%
        column_spec(5, width = "4em") %>%
        column_spec(6, width = "4em") %>%
        column_spec(7, width = "4em") %>%
        column_spec(8, width = "6em") %>%
        column_spec(9, width = "4em") %>%
        column_spec(10, width = "4em") %>%
        column_spec(11, width = "4em") %>%
        column_spec(12, width = "4em") %>%
       # collapse_rows(columns = 2, valign = "top",row_group_label_position = 'stack') 
       # collapse_rows(1:2, row_group_label_position = 'stack') %>%
    landscape()
```





