---
title: "Untitled"
date: "12/06/2019"
output:
  revealjs::revealjs_presentation:
    background_transition: none
    center: yes
    css: gk_css.css
    fig_caption: yes
    fig_height: 5
    fig_width: 10
    highlight: pygments
    incremental: yes
    reveal_options:
      previewLinks: yes
      slideNumber: yes
    reveal_plugins:
    - notes
    - search
    - chalkboard
    self_contained: no
    theme: sky
    transition: none
  prettydoc::html_pretty:
    highlight: github
    theme: cayman
subtitle: ' Subytitle for my project'
auther: ' Diesel Wing'
---

<!---
theme specifies the theme to use for the presentation (available themes are "default", "simple", "sky", "beige", "serif", "solarized", "blood", "moon", "night", "black", "league" or "white").

highlight specifies the syntax highlighting style. Supported styles include "default", "tango", "pygments", "kate", "monochrome", "espresso", "zenburn", and "haddock". Pass null to prevent syntax highlighting.

center specifies whether you want to vertically center content on slides (this defaults to false).

smart indicates whether to produce typographically correct output, converting straight quotes to curly quotes, --- to em-dashes, -- to en-dashes, and ... to ellipses. Note that smart is enabled by default.
transition specifies the visual effect when moving between slides. Available transitions are "default", "fade", "slide", "convex", "concave", "zoom" or "none".

background_transition specifies the background transition effect when moving between full page slides. Available transitions are "default", "fade", "slide", "convex", "concave", "zoom" or "none".
You can override the global transition for a specific slide by using the data-transition attribute, for example:

## Use a zoom transition {data-transition="zoom"}

## Use a faster speed {data-transition-speed="fast"}
You can also use different in and out transitions for the same slide, for example:

## Fade in, Slide out {data-transition="slide-in fade-out"}

## Slide in, Fade out {data-transition="fade-in slide-out"}


## CSS color background {data-background=#ff0000}

## Full size image background {data-background="background.jpeg"}

## Video background {data-background-video="background.mp4"}

## Embed a web page as a background {data-background-iframe="https://example.com"}


--->

# Reason for this presentation

To make a draft reveal
> - Eat eggs
> - Drink coffee

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

---

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## CSS color background {data-background=#ff0000}

## Full size image background {data-background="figure2b.png"}

```{r, echo = FALSE}
library(ggpubr)
# Grouped Scatter plot with marginal density plots
ggscatterhist(
  iris, x = "Sepal.Length", y = "Sepal.Width",
  color = "Species", size = 3, alpha = 0.6,
  palette = c("#00AFBB", "#E7B800", "#FC4E07"),
  margin.params = list(fill = "Species", color = "black", size = 0.2)
  ) + theme_transparent()
```  

## Video background {data-background-video="demo.mp4"}


## Embed a web page as a background {data-background-iframe="https://example.com"}

```{r, echo = FALSE}
library(tidyverse)
library("ggalt")
ggplot(mtcars, aes(mpg, wt)) +
  geom_point( aes(size = qsec , fill = cyl ), alpha = 0.5) +
  scale_size(range = c( 0.5,  12 ))  # Adjust the range of points size
```  


## Slide with R Code and Output

```{r, echo = FALSE}
library(tidyverse)
library("ggalt")
circle.df <- iris %>% filter(Species == "setosa")
ggplot(iris, aes(Petal.Length, Petal.Width)) +
    geom_point(aes(colour = Species)) + 
  geom_encircle(data = circle.df, linetype = 2)
```

## Slide with Plot

```{r, echo=FALSE}
library(ggforce)
ggplot(iris, aes(Petal.Length, Petal.Width, colour = Species)) +
    geom_point() +
    facet_zoom(x = Species == "versicolor")
```

# The top p head

## Background Three {.SlideClass #SlideID3}

Full screen background

```{r results='asis',echo=FALSE}

#makeBG(id='Slide3', 'figure2b.png')
```

```{r}
Sys.setlocale("LC_CTYPE", "russian")
#st_options(lang = 'ru')
#Then, to go back to default settings:

Sys.setlocale("LC_CTYPE", "")
#st_options(lang = "en")
```


## fdfkladfhj

## table

```{r, echo= FALSE}
library(knitr)
library(kableExtra)
dt <- mtcars[1:5, 1:6]

iris[1:10, ] %>%
  mutate_if(is.numeric, function(x) {
    cell_spec(x, bold = T, 
              color = spec_color(x, end = 0.9),
              font_size = spec_font_size(x))
  }) %>%
  mutate(Species = cell_spec(
    Species, color = "white", bold = T,
    background = spec_color(1:10, end = 0.9, option = "A", direction = -1)
  )) %>%
  kable(escape = F, align = "c") %>%
  kable_styling(c("striped", "condensed"), full_width = F)

kable(dt) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "float_right", font_size = 7)


```

## combineing formatable with 

```{r, echo= FALSE}
library(formattable)
mtcars[1:5, 1:4] %>%
  mutate(
    car = row.names(.),
    mpg = color_tile("white", "orange")(mpg),
    cyl = cell_spec(cyl, angle = (1:5)*60, 
                    background = "red", color = "white", align = "center"),
    disp = ifelse(disp > 200,
                  cell_spec(disp, color = "red", bold = T),
                  cell_spec(disp, color = "green", italic = T)),
    hp = color_bar("lightgreen")(hp)
  ) %>%
  select(car, everything()) %>%
  kable(escape = F) %>%
  kable_styling("hover", full_width = F) %>%
  column_spec(5, width = "3cm") %>%
  add_header_above(c(" ", "Hello" = 2, "World" = 2))
```
