---
title: "Report on Spring Failures"
subtitle: "Failures of Coil Springs and Air Springs : An Analysis"
author: "Gopal Kumar"
date: "`r Sys.Date()`"
output: tint::tintBook
bibliography: skeleton.bib
link-citations: yes
---

```{r setup, include=FALSE}
library(tint)
# invalidate cache when the package version changes
knitr::opts_chunk$set(tidy = FALSE, cache.extra = packageVersion('tint'))
options(htmltools.dir.version = FALSE)
```

# The main figure now

```{r fig-nocap-margin-first, fig.margin=FALSE, fig.width=8, fig.height=4, cache=TRUE, echo=FALSE}
library(ggplot2)

ggplot(mtcars, aes(wt, mpg)) + 
  geom_point(size=3, aes(colour=factor(cyl))) + 
  theme(legend.position="none")

```




Support _italic_ aka *em* and **strong**,  `code` snippets.


# Introduction

The Tufte handout style is a style that Edward Tufte uses in his books and handouts. Tufte's style is known for its extensive use of sidenotes, tight integration of graphics with text, and well-set typography. 
See footnote^[See Github repositories [tufte-latex](https://github.com/tufte-latex/tufte-latex) and [**mygithubrepository**](https://github.com/ggmtech].

You may use `tufte_handout` format for handouts, and `tufte_book` for books, `tufte_html` for html. 
See the book  @R-rmarkdown.

```yaml
---
title: "An Example Using the Tufte Style"
author: "John Smith"
output:
  tufte::tufte_handout: default
  tufte::tufte_html: default
---
```

There are two goals of this package:

1. To produce both PDF and HTML output with similar styles from the same R Markdown document;
1. To provide simple syntax to write elements of the Tufte style such as side notes and margin figures

For margin figure use `fig.margin = TRUE` unlike `\begin{marginfigure} \end{marginfigure}` 
or `<span class="marginfigure"> </span>`; .


# Headings


`r newthought('In his later books')`^[[Beautiful Evidence](https://www.edwardtufte.com/tufte/books_be)], Tufte starts each section with a bit of vertical space, a non-indented paragraph, and sets the first few words of the sentence in small caps. 

Use `newthought()` in an _inline R expression_ `` `r ` `` as demonstrated^[Note you should not assume **tufte** has been attached to your R session. You should either `library(tufte)` in your R Markdown document before you call `newthought()`, or use `tint::newthought()`.]

# Figures

## Margin Figures

chunk option `fig.margin = TRUE`. For example:

```{r fig-margin, fig.margin = TRUE, fig.cap = "MPG vs hp, color by transmission.", fig.width=3.5, fig.height=3.5, cache=TRUE}
library(ggplot2)
mtcars2 <- mtcars
mtcars2$am <- factor( mtcars$am, labels = c('automatic', 'manual')  )
ggplot(mtcars2, aes(hp, mpg, color = am)) +
              geom_point() + geom_smooth() +
              theme(legend.position = 'bottom')
```

The `fig.cap` chunk option to provide a figure caption. 

## Arbitrary Margin Content

In fact, you can include anything in the margin using the **knitr** engine named `marginfigure`. 
Unlike R code chunks ```` ```{r} ````, you write a chunk starting with ```` ```{marginfigure} ```` instead, then put the content in the chunk. See an example on the right about the first fundamental theorem of calculus.

```{marginfigure}
We know from _the first fundamental theorem of calculus_ that for $x$ in $[a, b]$:
$$\frac{d}{dx}\left( \int_{a}^{x} f(u)\,du\right)=f(x).$$
```

keep the margin content as simple as possible (syntax-wise) in the `marginefigure` blocks for html pdf interchang.  refrain from using footnotes, citations, or block-level elements (e.g. blockquotes and lists) there.

## Full Width Figures

chunk option `fig.fullwidth = TRUE`.

```{r fig-fullwidth, fig.width = 10, fig.height = 2, fig.fullwidth = TRUE, fig.cap = "A full width figure.", warning=FALSE, cache=TRUE}
ggplot(diamonds, aes(carat, price)) + geom_smooth() +
  facet_grid(~ cut)
```

Usually `fig.width` is large and `fig.height` is small. In the above example, the plot size is $10 \times 2$.

## Main Column Figures

Figures constrained to the main column is the default for LaTeX/HTML output.

```{r fig-main, fig.cap = "A figure in the main column.", cache=TRUE}
ggplot(diamonds, aes(cut, price)) + geom_boxplot()
```

# Sidenotes

 Any  footnote will automatically converted to a sidenote. ^[Footnote on sidenote as default] 

For ancillary information in the margin without the sidenote mark use the `margin_note()`  inline R expression. `r margin_note("This is a margin note.  Notice that there is no number preceding the note.")` 
but  Markdown syntax will not work here else use the `marginfigure` .

# References

cite R here [@R-base]. To enable this feature, you must set `link-citations: yes` in the YAML metadata
To check the version of `pandoc-citeproc` in your system, you may run this in R:

```{r eval=FALSE}
system2('pandoc-citeproc', '--version')
```

If your version of `pandoc-citeproc` is too low, or you did not set `link-citations: yes` in YAML, references in the HTML output will be placed at the end of the output document.

# Tables

Use with `kable()` . The table captions are placed in the margin like figures in the HTML output.

```{r}
knitr::kable( mtcars[1:6, 1:6], caption = 'A subset of mtcars.' )
```

# Block Quotes

Start with `>` are converted to block quotes. 
To right-aligned footer for the quote, you may use the function `quote_footer()` eg

> "If it weren't for my lawyer, I'd still be in prison. It went a lot faster with two people digging."
>
> `r tint::quote_footer('--- Joe Martin')`



# More Examples

Two plots in one figure environment with the chunk option `fig.show = 'hold'`:

```{r fig-two-together, fig.cap="Two plots in one figure environment.", fig.show='hold', cache=TRUE}
p <- ggplot(mtcars2, aes(hp, mpg, color = am)) +
  geom_point()
p
p + geom_smooth()
```

Then two plots in separate figure environments (the code is identical but the chunk option is the default `fig.show = 'asis'` now):

```{r fig-two-separate, ref.label='fig-two-together', fig.cap=sprintf("Two plots in separate figure environments (the %s plot).", c("first", "second")), cache=TRUE}
```

The two figures have different captions, and that is because we used a character vector of length 2 for the chunk option `fig.cap` (something like `fig.cap = c('first plot', 'second plot')`).

Mltiple plots in margin figures with two plots in the same figure environment in the margin:

```{r fig-margin-together, fig.margin=TRUE, fig.show='hold', fig.cap="Two plots in one figure environment in the margin.", fig.width=3.5, fig.height=2.5, cache=TRUE}
p
p + geom_smooth(method = 'lm')
```

Then two plots from the same code chunk placed in different figure environments:

```{r fig-margin-separate, fig.margin=TRUE, fig.cap=sprintf("Two plots in separate figure environments in the margin (the %s plot).", c("first", "second")), fig.width=3.5, fig.height=2.5, cache=TRUE}
knitr::kable(head(iris, 15))
p
knitr::kable(head(iris, 12))
p + geom_smooth(method = 'lm')
knitr::kable(head(iris, 5))
```

We blended some tables in the above code chunk only as _placeholders_ to make sure there is enough vertical space else they will be stacked tightly together. 

figures with no captions below in the margin, in the main column, and in full width, respectively.

```{r fig-nocap-margin, fig.margin=TRUE, fig.width=3.5, fig.height=2, cache=TRUE}
# a boxplot of weight vs transmission; this figure
# will be placed in the margin
ggplot(mtcars2, aes(am, wt)) + geom_boxplot() +
  coord_flip()
```
```{r fig-nocap-main, cache=TRUE}
# a figure in the main column
p <- ggplot(mtcars, aes(wt, hp)) + geom_point()
p
```
```{r fig-nocap-fullwidth, fig.fullwidth=TRUE, fig.width=10, fig.height=3, cache=TRUE}
# a fullwidth figure
p + geom_smooth(method = 'lm') + facet_grid(~ gear)
```

# Some Notes on Tufte CSS

Use `r sans_serif('sans-serif fonts')`, use  `sans_serif()` in **tufte**. 

For epigraphs,use a pair of underscores to make the paragraph italic in a block quote, e.g.

> _I can win an argument on any topic, against any opponent. People know this, and steer clear of me at parties. Often, as a sign of their great respect, they don't even invite me._
>
> `r quote_footer('--- Dave Barry')`


To see the R Markdown source  follow [this link to Github](https://github.com/eddelbuettel/tint/blob/master/inst/rmarkdown/templates/pdf/skeleton/skeleton.Rmd), use the wizard in RStudio IDE (`File -> New File -> R Markdown -> From Template`), or open the Rmd file in the package:

```{r eval=FALSE}
file.edit(
  tint:::template_resources(
    'tint', '..', 'skeleton', 'skeleton.Rmd'
  )
)
```

```{r bib, include=FALSE}
# create a bib file for the R packages used in this document
knitr::write_bib(c('base', 'rmarkdown'), file = 'skeleton.bib')
```
