\documentclass[11 pt, a4paper]{report}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[survey]{automultiplechoice}
%\usepackage{automultiplechoice}
\AMCtext{draft}{}
%\AMCtext{message}{Worker’s Inquiry}

\begin{document}
\begin{Questionnaires}{1}
my first questionnaire
\end{Questionnaires}

\begin{Questionnaires}{1}
Question 1: Does the shop in which you work belong to a capitalist or to a limited company?
\begin{variable-single}{shop}{99}
\answer{capitalist}{0,3}{vallab-sc}{checkbox-sc}\scoring{b=3}
\answer{limited company}{0,2}{vallab-sc}{checkbox-sc}\scoring{b=2}
\answer{don’t know}{0,1}{vallab-sc}{checkbox-sc}\scoring{b=1}
\end{variable-single}
\end{Questionnaires}


\begin{Questionnaires}{1}
Question 2: What is the youngest age at which children are taken on?
\begin{variable-single}{childage}{99}
\answer{< 13 \\ years}{0,0}{vallab-sc, align=center}{checkbox-sc, below=of lab\thecsvrow}\scoring{b=1}
\answer{13 \\ years}{2,0}{vallab-sc, align=center}{checkbox-sc, below=of lab\thecsvrow}\scoring{b=2}
\answer{14 \\years}{4,0}{vallab-sc, align=center}{checkbox-sc, below=of lab\thecsvrow}\scoring{b=3}
\answer{15 \\years}{6,0}{vallab-sc, align=center}{checkbox-sc, below=of lab\thecsvrow}\scoring{b=4}
\answer{16 \\years}{8,0}{vallab-sc, align=center}{checkbox-sc, below=of lab\thecsvrow}\scoring{b=5}
\answer{> 16 \\years}{10,0}{vallab-sc, align=center}{checkbox-sc, below=of lab\thecsvrow}\scoring{b=6}
\answer{don’t \\know}{13,0}{vallab-sc, align=center}{checkbox-sc, below=of lab\thecsvrow}\scoring{b=7}
\end{variable-single}
\end{Questionnaires}

\end{document}













\documentclass{article}
\usepackage{textcomp,amsmath,longtable}
\usepackage{latexsym}


\begin{document}

\subsection*{About you}
\label{sec:about-you-rest2}

\begin{itemize}    
\item \textbf{Your Email} 
\\
  \small{(The email field is required to keep track
  of the answers. All results will be anonymised when used.)}

\item \textbf{Your Age}
\item \textbf{Your Gender} $\Box$ F $\Box$ M
\end{itemize}

\subsection*{About the Conversation}
\label{sec:about-conversation-rest2}

The following questions are given in the form of statements regarding
the computer during its interaction. We would like you to give your
level of agreement with each statement on a scale going from "Strongly
Disagree" to "Strongly Agree".    

\begin{itemize}

\item \textbf{I found the fact that the computer acted as if it knew me was irritating.}\\$\Box$ Strongly disagree $\Box$ Disagree $\Box$
  Neither agree nor disagree $\Box$ Agree $\Box$ Strongly Agree

\item \textbf{In this conversation, the computer interacted with you
    in a natural way. }\\$\Box$ Strongly disagree $\Box$ Disagree
  $\Box$ Neither agree nor disagree $\Box$ Agree $\Box$ Strongly Agree

\item ....
\end{itemize}

%% Set up counters for questions
\newcounter{qnumber}
\setcounter{qnumber}{0}
\stepcounter{qnumber}
\newcommand{\yesno}{\textsf{Yes}~~\textsf{No} {\Large ~$\Box$}~~~~   {\Large $\Box$}}

%% we now define the questions
\newcommand{\question}[1]{
  \hfill \relax1.\theqnumber\hfill\hfill &\textsf{#1} &{\small\yesno} & {\small\yesno} &{\small\yesno}\stepcounter{qnumber}\\ \hline
  }
  
%% we now define the questions
\newcommand{\heading}[1]{
    1.0 &\multicolumn{4}{|l|}{\bf\textsf{#1}}\\ \hline %
    }
      \newcommand{\divider}{\hline}
      \begin{longtable}{|c| p{5.61cm}|p{1.5cm}|p{1.5cm}|  p{1.55cm} |}
      \divider
      Sl.     &Quality Checks & A     & B     &C\\
      \divider\divider
\heading{Installation}
      \question{Are the fans installed as per the drawings and specifications?}
      \question{Are all safety rules understood by personnel repsonsible for operating the equipment?}
      \heading{Electrical}
      \question{Proper motor and fan rotation verified?}
      \question{Verify that proper disconnect is located within sight of the unit it controls.}
      \question{does your name starts with G}
\heading{Electrical}
      \question{Proper motor and fan rotation verified?}
      \question{Verify that proper disconnect is located within sight of the unit it controls.}
      \end{longtable}
      
      \end{document}