# Yuhi Rmd notes

The slides from https://slides.yihui.org/2019-DahShu-rmarkdown.html#1

# 1 Why use TinyTeX?

They are all too big: TeX Live, MiKTeX, MacTeX (~5Gb). TinyTeX (yihui.org/tinytex) is ~150Mb when installed:

tinytex::install_tinytex()
With the R function tinytex::latexmk(), two common LaTeX problems are automatically solved:

Missing LaTeX packages are automatically installed (doesn't require IT).
The .tex document is compiled for the correct number of times to resolve cross-references (e.g., pdflatex + bibtex + makeidx + pdflatex + pdflatex).

Demo: 01-tinytex.Rmd

# 2. Generate a report from an R script

' Write your narratives after #'.
' Of course, you can use **Markdown**.
' Write R code in the usualy way.

1 + 1
str(iris)

#' Need chunk options? No problem.
#' Write them after #+, e.g.,
#+ fig.width=5

plot(cars)
The script is converted to Rmd through knitr::spin(); then rmarkdown::render() will render the Rmd

Demo: 02-spin.R (either click the "Notebook" button in

# 3. Convert Rmd to R script
Demo: 03-purl.Rmd

knitr::purl("03-purl.Rmd")  # output: 03-purl.R
# no documentation, pure code
knitr::purl("03-purl.Rmd", documentation = 0)
# full documentation in #' comments
knitr::purl("03-purl.Rmd", documentation = 2)

# 4. Add citations

BibTeX databases:

knitr::write_bib("base", file = "")
 @Manual{R-base,
  title = {R: A Language and Environment for Statistical Computing},
  author = {{R Core Team}},
  organization = {R Foundation for Statistical Computing},
  address = {Vienna, Austria},
  year = {2019},
  url = {https://www.R-project.org/},
}


Use @key to cite an entry (or [@key] if you need brackets, or cite multiple entries via [@key-1; @key-2])

# 5. Cross-reference figures, tables, and sections
With the bookdown package (even if you are not writing a book), you can cross-reference things via \@ref(key).

A few possible bookdown output formats:

output:
  - bookdown::html_document2
  - bookdown::pdf_document2
  - bookdown::word_document2
  
Demo: 05-cross-reference.Rmd

# 7 Line breaks (not paragraphs)
Line break in the output? : two trailing spaces before you break a line in the source.
In HTML <br/> and in LaTeX use \\ 

If you want to preserve the line breaks as in poems or lyrics.

# 8. Put all code in the appendix

The key: the chunk option ref.label to reference other code chunks.

More info: https://yihui.org/en/2018/09/code-appendix/

Demo: 08-code-appendix.Rmd

You can move your code freely in an Rmd document using ref.label, without cut-and-paste.

# 9. Create an animation
To create a GIF animation from all R plots in a code chunk, install the gifski package. Then use the chunk option animation.hook='gifski':

```{r, animation.hook='gifski', eval=FALSE, echo=TRUE}
for (i in 1:2) {
  pie(c(i %% 2, 6), col = c('red', 'yellow'), labels = NA)
}
```


# 10. Cache time-consuming code chunks
Use the chunk option cache = TRUE if a code chunk is time-consuming and the code doesn't change often.

# 11. Add logos to your R plots
The key: the chunk option fig.process can be a function to post-process your plots.

```{r, fig.process=function(x, options) { x }}
# plot
```
Demo: 11-magick.Rmd

# 12. Add real LaTeX math expressions to R plots
You may know ?plotmath, but these tricks in base R graphics do not produce real LaTeX math expressions

plot(cars, main = expression(hat(beta) == (X^t * X)^{-1} * X^t * y))
The (perhaps only) R package that allows you to write LaTeX expressions in R plots is tikzDevice.

How to use tikzDevice in R Markdown? Short answer: use the chunk option dev = "tikz". But...

Demo: 12-tikz.Rmd


# 13. Use other languages
Python, Julia, SQL, C++, shell scripts, JavaScript, CSS, ...

To know all languages supported in knitr (there are more than 40): names(knitr::knit_engines$get())

```{python}
x = 42
```
Demo: 13-lang.Rmd

# 14. Child documents
You can split your long documents into shorter ones, and include the shorter documents as child documents, e.g.,

```{r, child='one.Rmd'}
```

```{r, child=c('one.Rmd', 'two.Rmd')}
```


# 15. Start bookdown and blogdown projects

In RStudio: File -> New Project -> New Directory; select "Book" or "Website" projects.


Demo: 04-citation.Rmd

# Diagrammer

## Does not work in pdf : explore workaround

```{r}
library(DiagrammeR)
DiagrammeR::mermaid("
graph TB
  A-->B
  A-->C(testing  this lable)
  C-->E{A Rhombus}
  B-->D
  C-->D
  D-->F[Rectangle One]
  E-->F
")
```

```{r  }
library(DiagrammeR)
DiagrammeR::mermaid("
graph LR
A(Total RDSO items = 661 )-->B[Less then 3 Vendors = 221]
B-->C{ 1 Crores = 145 }
B-->D( 1 Crores = 76)
C-->E[Diminishing , No vendor interest = 118]
C-->F(Increasing, Develop Vendor  = 27)
D-->G[Obsolete, diminishing  = 35]
D-->H[New tech, increasing  = 41]
C-->G[Total for vendor development = 68]
")
```



```{r}
DiagrammeR::mermaid("
sequenceDiagram
  Vendor->>Web portal: ask appointment ticket
  Software ->>officer: check up schedule
  alt tickets available
    database->>ticket seller: ok
    ticket seller->>customer: confirm
    customer->>ticket seller: ok
    ticket seller->>database: book a seat
    ticket seller->>printer: print ticket
    feedback taker-->>formfilling:get feedback
  else sold out
    database->>ticket seller: none left
    ticket seller->>customer: sorry
  end
")
```